---
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  dev = "png"
  
)
```

# ggords

The package provides six functions: `ggpca()`, `ggca()`, `ggpcoa()`, `ggnmds()`, `ggrda()`, `ggcca()`.
You can customize the display labels and themes. Labels can contain formulas. Image themes can be set by themes in ggplots or by other packages(ggthemr).

## Installation

```{r eval=FALSE}
library(devtools)
install_github("wdy91617/ggords")
```

## Example Usage


```{r }
library(ggords)
require(vegan)
require(ggplot2)
data(Envs)

```

### get group factor

```{r} 

Env.w <- hclust(dist(scale(Envs)), "ward.D")
gr <- cutree(Env.w , k=4)
grl <- factor(gr)
```

## ggpca

### Compute PCA

```{r} 
Env.pca <- rda(Envs,scale = TRUE)
#head(summary(Env.pca))
```

### Produce a plot 

```{r fig.width=5, fig.height=4.5, fig.align = "center"} 
ggpca(Env.pca)

```

### Add a group

```{r fig.width=5, fig.height=4.5, fig.align = "center"}  
ggpca(Env.pca, group = grl) 

```

### Set a theme 

```{r fig.width=5, fig.height=4.5, fig.align = "center"}  
ggpca(Env.pca, group = grl, spacol = "white") + theme_dark()

```

### Set a theme (use ggthemr packages, more themes in ggthemer)
[](https://github.com/cttobin/ggthemr)
```{r fig.width=5, fig.height=4.5, fig.align = "center"} 
library(ggthemr)

chalk_theme <- ggthemr('chalk', set_theme = FALSE)
fd_theme <- ggthemr('flat dark', set_theme = FALSE)

p <- ggpca(Env.pca, group = grl, spacol = "white")
p + chalk_theme$theme
p + fd_theme$theme
```

### Remove the arrow

```{r fig.width=5, fig.height=4.5, fig.align = "center"} 
ggpca(Env.pca, group = grl, spearrow = NULL)
```

### Modify legend title, group color and point shape

```{r fig.width=5, fig.height=4.5, fig.align = "center"} 
ggpca(Env.pca, group = grl, spearrow = NULL) + 
  scale_color_manual(name = "Groups",values = c("red2", "purple1", "grey20","cyan")) +
  scale_shape_manual(name = "Groups",values = c(8,15,16,17))

```

### Add confidence ellipses

```{r fig.width=5, fig.height=4.5, fig.align = "center"} 
ggpca(Env.pca, group = grl, spearrow = NULL, ellipse = TRUE) +
  scale_colour_hue(l = 70, c = 300)

```


## ggpnmds

### Compute NMDS

```{r} 
Env.nmds <- metaMDS(Envs, distance="bray")
#head(summary(Env.nmds))
```

### Produce a plot 

```{r} 
ggnmds(Env.nmds)
```

### Add a group

```{r} 
ggnmds(Env.nmds, group = grl) 
```

### Set a theme 

```{r} 
ggnmds(Env.nmds, group = grl, spacol = "white") + theme_dark()

```

### Set a theme (use ggthemr packages, more themes in ggthemer)
[](https://github.com/cttobin/ggthemr)

```{r} 

library(ggthemr)

chalk_theme <- ggthemr('chalk', set_theme = FALSE)
fd_theme <- ggthemr('flat dark', set_theme = FALSE)

p <- ggnmds(Env.nmds, group = grl, spacol = "white")
p + chalk_theme$theme
p + fd_theme$theme
```


### Remove the arrow

```{r} 
ggnmds(Env.nmds, group = grl, spearrow = NULL)
```

### Set labels

```{r} 
mlabs<-c("NH[4]^{`+`}" , "NO[3]^{`-`}" ,"delta^13*C","A[1]","sqrt(2*pi)","frac(x^2,2)",
         "sin(x)","hat(x)","bar(xy)","90*degree","x^{y+z}")

ggnmds(Env.nmds, group = grl, spearrow = NULL, msplabs = mlabs)
```

### Modify legend title, group color and point shape

```{r} 
ggnmds(Env.nmds, group = grl, spearrow = NULL) + 
  scale_color_manual(name = "Groups",values = c("red2", "purple1", "grey20","cyan")) +
  scale_shape_manual(name = "Groups",values = c(8,15,16,17))
```

### Add confidence ellipses

```{r} 
ggnmds(Env.nmds, group = grl, spearrow = NULL, ellipse = TRUE) +
  scale_colour_hue(l = 70, c = 300)
```

License
-------
Released under GPL-3.